Draft Exploration

### 2020-04-21 draft_exploration.Rmd
messing with US map

```{r}
state_mlb %>%
  filter(big_state == 0) %>%
  ggplot(aes(full, drafted, color = percent_mlb)) +
  coord_flip() +
  geom_point() +
  scale_y_continuous(breaks = c(0, 50, 100, 200, 300)) +
  scale_color_viridis_c() +
  labs(
    x = "State",
    y = "Number of Players Drafted",
    title = "Number of High School Players Drafted by State",
    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
    color = "MLB Percent"
  )
```

>>>>

```{r, echo=FALSE}
state_mlb %>%
  filter(big_state == 0) %>%
  ggplot(aes(full, drafted, color = percent_mlb)) +
  coord_flip() +
  geom_point() +
  scale_y_continuous(breaks = c(0, 50, 100, 150, 200, 250, 300, 350)) +
  theme_gray() +
  theme(axis.text.y = element_text(size = 7.5)) +
  scale_color_viridis_c() +
  labs(
    x = "State",
    y = "Number of Players Drafted",
    title = "Number of High School Players Drafted by State",
    subtitle = "From 1965-2012 - Outliers: (California: 2249, Texas: 627, Florida: 1069)",
    color = "MLB Percent"
  )
```

```{r, include=FALSE}
master %>%
  filter(source == "H" & draft_numb == 1 & high_level == "MLB" & signed == "Y") %>%
  filter(draft_region_id == "MT") %>%
  arrange(desc(year)) %>%
  select(year, draft_round, teamname, first_name, last_name, mlb_length)
```
